Intro Seminar

### 2017-03-12 doc/seminar2017.Rmd
Fixed acr variable syntax error
Added baseline 25(OH)D scatterplot

ds %>% 
  filter(!(acr_status == "Macroalbuminuria")) %>% 
  cor.test(formula = ~ eGFR + udbpCrRatio, data = ., method = "spearman")
```

@@

>>>>

ds %>% 
  filter(!(acrStatus == "Macroalbuminuria")) %>% 
  cor.test(formula = ~ eGFR + udbpCrRatio, data = ., method = "spearman")
```

@@

## Vitamin D

```{r VitD scatterplot}

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  dplyr::select(VitaminD, udbpCrRatio) %>% 
  scatter_plot("log(udbpCrRatio)", "VitaminD",
               "log UDBP:Creatinine",
               "Serum 25(OH)D",
               line = TRUE)

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  cor.test(formula = ~ udbpCrRatio + VitaminD, data = ., method = "spearman")
```
